multiset_hyper2

### 2023-01-05 inst/multiset_hyper2.Rmd
label all chunks
reflect change to how rp() works, now fillup() not needed

```{r,exactingtest,cache=TRUE}
rs <- fillup(rp(100,dirichlet(c(a=1,b=1,c=1)))) # random strengths
colnames(rs) <- letters[1:3]
head(rs)
f <- function(s){
  jj <- s
  names(jj) <- letters[1:3]
  tfun(help=1:3,strength=jj,M=M)
}
x <- apply(rs,1,f)
```

```{r}
hist(x-mean(x))
```

>>>>

```{r,exactingtest,cache=TRUE}
rs <- rp(100,dirichlet(c(a=1,b=1,c=1))) # random strengths
colnames(rs) <- letters[1:3]
head(rs)
f <- function(s){
  jj <- s
  names(jj) <- letters[1:3]
  tfun(help=1:3,strength=jj,M=M)
}
x <- apply(rs,1,f)
```

```{r,plotdifferences}
hist(x-mean(x))
```
